Bipartite Fidelity and Loschmidt Echo of Bosonic Conformal Interface

### 2017-10-13 reply_to_referee.tex

The content of this reply is supplemented in App. C. We request the referee to reconsider the presented arguments.
}

(2) I also find the whole presentation of the mapping unsatisfactory. In part, this has to with the fact that no lengths are indicated in the figures.

For the fidelity, one maps in Fig. 5 the initial strip to an annulus with inner and outer radii determined by the length of the strip which goes to infinity. Then one moves the point, where the boundary condition changes, to the origin, which means that, in the strip, it is moved to the far left and disappears there. I cannot see, how the calculation then proceeds. In [25], a different conformal map was used.

\reply{
We have added more descriptions in the text around Fig.5 and Fig.6 about the conformal mappings used there. One major change is Fig 5. We do not impose IR regulator(previously a vertical line at $x = W$)  on the left panel of the slit diagram, but do add the small semi-circle. After doing the conformal mapping to the center diagram, we end up with a corner centered at $\xi = 1$ with round tip. To evaluate this diagram, we add another semi-circle centered at $\xi = 1$ with radius $R_{\xi}$. This should avoid the problem the referee was worrying about.

(We add the semi-circle manually in the center of Fig. 5, which is incidentally in close analogy to the treatment of the truncated cone and corner in the Cardy-Peschel paper. So to get the correct result, we should subtract its contribution to the free energy, which is exactly what we do in App. C.)

The annulus diagrams in both Fig. 5 and Fig. 6 are not strictly concentric to higher order corrections of $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$. To resolve this problem, (which the referee maybe worried about), we notice the following fact
\begin{itemize}
\item the conformal map from the non-concentric circles to the cylinder diagram exists: this can be done by first mapping the non-concentric circles to concentric circles and then use the $\ln z$ map. 
\item the resulting width of the cylinder only depend on the cross ratio of the intersection points of the two circles w.r.t. the horizontal axis.
\end{itemize}
since the conformal mapping preserve the cross ratio, we can calculate the width of the cylinder in terms of the cross ratio in the non-concentric circles. The calculation we did use the first order approximation of the cross ratio, but is enough to get the leading order of the width of the cylinder correct. The higher order corrections are of order $\frac{\epsilon}{L}$ and $\frac{\epsilon}{\tau}$, which should not affect the power law scalings of the fidelity and echo.

@@

This line of argument is also included in the main text below Fig. 6. 
}

For the Loschmidt echo, the starting point is again a strip of width L, as shown in Fig. 4. However, in the left part of Fig. 6 this width no longer appears. There is only a small remark in the text that $L \gg \tau$. But L is of significance, for finite L the ratio t/L enters, and in Ref. [25] this case could actually be treated.

\reply{We declare in the text (after Eq. (16)) that we will take $L \gg t$ in all the echo computation. This keeps the problem with only one length scale.

  We are aware that such geometry with both finite $t$ and $L$ can be mapped to the upper half plane by the Schwarz-Christoffel maps, as demonstrated in Ref.[25]. But the conformal interface, the dashed line, will be inside the upper half plane and we don't know how to calculate its OPE with the stress tensor. So in this paper, we only aim to understand the leading order behavior and its relation to the transmission coefficient. }

In the center part, there are two half-circles around the origin, which supposedly are the images of those on the left. But their radii (which determine the parameter $\beta$) are not given anywhere.

@@

\reply{We take this identification because the boundary state computation is easier.

In fact, since the distance between the blue lines ($\sim \ln L , \ln \tau$) on the $w$ plane in Fig.6 is much larger than the distance between the two dashed lines, one can view rotate this cylinder diagram and consider an evolution between the blue lines. This is the point of view taken by our alternative approach (an $S$ modular transformation to the figure in the boundary state calculation), the leading term of free energy is then the groundstate energy of the Hamiltonian given the boundary conditions on the dashed line, multiply by $\beta$, see Eq.(B8).

If one impose different boundary conditions on the blue lines, the free energy then is not 
\begin{equation}
F = - \ln \text{tr}( e^{ - \beta H_{ab} } ) =  \beta  E_c
\end{equation}
but (for large $\beta$ as is the case here)
\begin{equation}
\begin{aligned}
F &= - \ln \langle \text{blue boundary state 1} | e^{ - \beta H_{ab}} | \text{blue boundary state 2} \rangle \\
&= \beta  E_c - \ln \langle \text{blue boundary state 1} | \text{ground state} \rangle \\
 &\quad - \ln \langle \text{blue boundary state 2} |\text{ ground state }\rangle                                                                                 
\end{aligned}
\end{equation}
where the additional terms can be viewed as Affleck-Ludwig boundary entropy that is subleading (independent of $\beta$) in the free energy.

As far as the leading order (in $\beta$) is concerned, the boundary conditions imposed on the blue line should not matter. We therefore take the simplest periodic boundary condition for the ease of computation.}

@@

\reply{
A clarification is indeed necessary. We here use the Hurwitz zeta function regularization and so H stands for Hurwitz.

The final results, after a careful check is correct, however, the $x^{-s}$ term should be $-(-x)^{-s}$ if the $n = 0$ term is handled properly. Thanks for pointing this out!}

I also think that Appendix E ("Alternative approach...") should come after the "actual" approach which is presented in Appendix F. There is also a typo in equ.(F9).

\reply{We have rearranged the order of appendixes as request. Now App. A is the calculation for the main analytic results. App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details.

We also fix the typo in Eq.(A9), where the $\frac{1}{6}$ should be $-\frac{1}{6}$.}

@@

(4) The main result, namely the variation of the exponents in Equ. (27) and Figs. 8-10 as functions of the parameter theta is not discussed. The increase with theta must have some kind of physical interpretation and also the particular values at theta=0 and theta=pi/2.

\reply{We add two paragraphs in the discussion section about the main results.

We first deal the three special points $\theta = 0, \frac{\pi}{4}, \frac{\pi}{2}$ and their special relations to the bcc operator ${\rm D} \rightarrow {\rm N}$, and then present a hand-waving argument that the quadratic relation should come from the dimension of the vertex operators.

@@

(6) A number of equations expressing these changes of boundary conditions appear several times in identical form: (22),(37),(40); (24),(30) and Fig.7; (18),(26),(32),(38) and Fig.8; (28),(34) and Fig.9; (36),(39) and Fig.10. This is a redundancy which should be reduced.

\reply{Question (5) and (6) are about the notations of boundary conditions.

We remove the redundant boundary condition c in the some of the equations as long as it is equal to a. The simplified notation like $\text{DN} \rightarrow \lambda$ is better to be perceived as a single boundary condition changing process and the associated bcc operator.

Since the notation is shortened, we don't let them occupy a single equation and instead put them inside a sentence. We believe that such redundancy can be tolerated given that the length of the this notation is comparable to the citation phrase ``in Eq.(XX)'', and the time it saves to look up. }

@@

(7) All References appear twice with different numbers! This must also be the reason, why the numbering in the text starts at 48. I am astonished that the authors did not notice that.

\reply{This is really embarrassing. We had 47 citations in our local version of manuscripts but 94 on the submission. We find that this is because our submission script flatex inserted all the input tex files (since the submission is easier with a single tex file) as well as all bbl files, resulting in the duplication of references.

@@

App. A is the calculation for the main analytic results. The reader shall only need this appendix to reproduce Eq.(23).

App. B/C are supplements to analytic results. Other appendices are for the numerical models and calculational details. We have also mentioned these structural changes in the end of the introduction.}

6) The last sentence before Sec. 4 states that the analytical (incorrect) and numerical curves "merge" at theta=0. In fact, these two curves are quite different and clearly the analytical curve cannot reproduce the numerics at all, as expected. To me it seems like that the green curve coincides with the dots in Fig. 10 only by chance. I'm not sure what the relevance of this curve is or mentioning that at theta=0 the numerics and the (incorrect) analytics "merge." This merging is simply because theta=0 is the no-quench point, when the pre- and post-quench setup is the same.

\reply{We have remove the sentence of ``merging'' at theta = 0. That is as the referee said only a calibrating point. But we do want to reserve the green curve as we (subjectively) believe the collapse is not a coincidence. The difference $1/8$› is a magic number that is twice of the majorana operator dimension, maybe indicating the structure of the 3-point function (the bcc operators between each pair of  a, b, c). We didn't write this speculation for the lack of evidence but do want to reveal this coincidence to inspire the readers.}

### 2017-10-13 analy_eval.tex
[referee] revise reply letter

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal mappings $\zeta(\xi)$ that map the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the result is the same if we use the cross ratio of the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently used the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

Since the fidelity and Loschmidt echo are both square of the amplitude, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.

The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order. Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
\end{equation}
Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution to project out only the groundstate $|0_{ab}\rangle $. Hence the free energy
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choice of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

Here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}. We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
\begin{equation}
\begin{aligned}
b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
\end{aligned}
\end{equation}
for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
\begin{equation}
\begin{aligned}
\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^T, \quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^T\\
\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^T, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^T .
\end{aligned}
\end{equation}
The boundary state in Eq.~\eqref{eq:bd_state} is then 
\begin{equation}
\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
\begin{pmatrix}
  \vec{\bar{b}}_1^{\dagger}\\
  \vec{\bar{b}}_2^{\dagger}
\end{pmatrix}\Big\}  |0  \rangle ,
\end{equation}
where $R_a( \theta ) = -S_a \times \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )$, we have
\begin{equation}
|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
\end{equation}

@@

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

>>>>

One subtlety of the above description is that the two semi-circles in the center diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not precisely concentric. This can be resolved by the following observation. There exists conformal map $\zeta(\xi)$ that maps the non-concentric circles to two standard concentric circles of radii $1$ and $R$ ($R>1$) on the $\zeta$ plane\cite{brown_complex_2009}. Then the logarithmic map $w = \ln \zeta$ produces a cylinder of width $\ln R$. In our case, the width of the cylinder is a conformal invariant that only depends on the cross ratio of the half annulus. The four intersection points of two standard concentric circles on $\zeta$ plane are $(\pm 1,0)$ and $(\pm R,0)$, whose cross ratio is
\begin{equation}
\eta = \frac{(1 + R)^2}{(1 - R)^2}. 
\end{equation}
Hence the width of the cylinder is $\ln \frac{\sqrt{ \eta } - 1}{\sqrt{ \eta} + 1}$. Since conformal transformation preserves the cross ratio, the same expression can be used on the slightly non-concentric diagrams of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, provided we use the intersection points there to calculate the cross ratio. The calculation in Eq.~\eqref{eq:fidel_cyd_width} and Eq.~\eqref{eq:echo_cyd_width} equivalently uses the leading order approximation to $\eta$ in the respective geometry and thus get the leading order term in the width of the cylinder. The slight deviation to the precise concentric geometry will only bring $\frac{\epsilon}{L}, \frac{\epsilon}{\tau}$ corrections to the width parameter and will not affect the fidelity and echo exponents.

Since the fidelity and Loschmidt echo are both square of the amplitudes, we should set the width of the cylinder $\beta = 2 \ln L$ or $ 4 \ln \tau$ after obtaining the partition function on it.

The actual boundary conditions on the blue lines -- the regulators in Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold} are not important in the leading order. Taking Fig.~\ref{fig:H-tau_fold} for example, we can alternatively view the right panel as the amplitude between the two blue boundary states by a Hamiltonian with boundary condition $a$ and $b$
\begin{equation}
Z_{ab} =  \langle 1 | e^{ - \beta H_{ab}} | 2 \rangle  .
\end{equation}
Since $\beta$ --the width of the cylinder is large in this problem, we expect that the imaginary time evolution will project out only the groundstate $|0_{ab}\rangle $. Hence the free energy is
\begin{equation}
\begin{aligned}
F &=  - \ln Z_{ab}  \sim - \ln \langle 1 |0_{ab} \rangle \langle   0_{ab}  |e^{ - \beta H_{ab}}|0_{ab} \rangle \langle 0_{ab} | 2 \rangle \\
&= \beta  E_c - \ln \langle 1| 0_{ab} \rangle  - \ln \langle 0_{ab}  |2 \rangle,
\end{aligned}
\end{equation}
where $E_c$ is the groundstate energy of $H_{ab}$. We see that different choices of the boundary conditions only change the term independent of $\beta$. Thus in the leading order we can choose any boundary condition. The one we pick is the simplest one: the periodic boundary condition that identifies the two blue lines.

With these in mind, here we set up the partition function calculation of the general process $S_a( \theta_1 ) \rightarrow S_b( \theta_2)$ and leave the technical details to App.~\ref{app:lambda_12}. We define a set of bosonic operators related to the $a^i_n$s in Eq.~\eqref{eq:di_mode_expansion} through
\begin{equation}
\begin{aligned}
b^i_n &= \frac{a^i_n}{\sqrt{n}} \quad (b^i_n)^{\dagger} &= \frac{a^i_{-n}}{\sqrt{n}} \\
\bar{b}^i_n &= \frac{\bar{a}^i_n}{\sqrt{n}} \quad (\bar{b}^i_n)^{\dagger} &= \frac{\bar{a}^i_{-n}}{\sqrt{n}} \\
\end{aligned}
\end{equation}
for $n > 0 , i = 1, 2$, and group them compactly with the vector notation
\begin{equation}
\begin{aligned}
\vec{b}_i &= ( b^i_1, b^i_2, \cdots )^\top, \qquad \,\,\quad \vec{\bar{b}}_i = ( \bar{b}^i_1, \bar{b}^i_2, \cdots )^\top\\
\vec{b}^\dagger_i &= ( (b^i_1)^\dagger, (b^i_2)^\dagger, \cdots )^\top, \quad\vec{\bar{b}}^{\dagger}_i = ( (\bar{b}^i_1)^\dagger, (\bar{b}^i_2)^\dagger, \cdots )^\top.
\end{aligned}
\end{equation}
The boundary state in Eq.~\eqref{eq:bd_state} is then 
\begin{equation}
\exp\Big\{  (\vec{b}_1^{\dagger} \vec{b}_2^{\dagger} ) R_a( \theta )   
\begin{pmatrix}
  \vec{\bar{b}}_1^{\dagger}\\
  \vec{\bar{b}}_2^{\dagger}
\end{pmatrix}\Big\}  |0  \rangle ,
\end{equation}
where $R_a( \theta ) = -S_a \otimes \mathbb{I}$. Using even a lazier notation $\vec{b} = ( \vec{b}_1, \vec{b}_2 )^\top$, we have
\begin{equation}
|a \rangle = \exp\Big\{  \vec{b}^{\dagger} R_a( \theta )    \vec{\bar{b}}^{\dagger} \Big\} |0 \rangle .
\end{equation}

@@

In App.~\ref{app:lambda_12}, we obtained the leading order term in the free energy associated with Eq.~\eqref{eq:Zab-bd}. This expression is also obtained by an alternative Casimir energy calculation in App.~\ref{app:gnd_dn_lambda} for one set of the boundary conditions. A na\"ive application of the result however will lead to an apparent contradiction. One notable example is that when $a = b  = {\rm P}$, the free energy given by App.~\ref{app:lambda_12} is $- \frac{1}{12}\beta$, which should actually be {\it zero} because this is the (regularized) free energy on a plane without any interface. Physically this corresponds to the situation that the boundary condition does not change after joining the two chains. Hence the Loschmidt echo will stay at $1$ and the free energy is $0$. This motivates a shift to the free energy
\begin{equation}
\mathcal{F} = - \ln Z_{ab} ( \beta ) + \frac{1}{12} \beta ,
\end{equation}
where $\frac{1}{12}\beta$ is the value of $ \ln Z_{ab} ( \beta )$ when $a = b = {\rm P}$. A more careful inspection in App.~\ref{app:F_correction} shows the origin of the shift: part of it comes from the outer semi-circles in the middle panel of Fig.~\ref{fig:fidel-map} and Fig.~\ref{fig:H-tau_fold}, and part comes from the non-homogeneous term in the conformation transformation of the stress tensor from annulus to cylinder.

### 2017-10-13 disc.tex
[referee] revise reply letter

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}. We can first understand the values of several special points on this curve. 
\begin{itemize}
\item $\theta = 0$: This is where the boundary condition does not change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
\item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$. The chain is still disconnected after the change of the boundary condition. We can thus view the problem of changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D. The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimension is $\Delta = \frac{1}{16}$. From this we can get the exponent to be $\frac{1}{2}$
\begin{equation}
\begin{aligned}
  \quad \mathcal{L}(\tau) &\sim |\langle \phi_{{\rm D N}}(0) \phi_{{\rm ND}}(\tau)   \rangle |^2 
|\langle \phi_{{\rm ND}}(0)  \phi_{{\rm DN}}(\tau)   \rangle| ^2\\
& \sim \frac{1}{|\tau|^{8\Delta}} = \frac{1}{|\tau|^{\frac{1}{2}}},
\end{aligned}
\end{equation}
which agrees with our results. 
\item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$. The exponent $\frac{3}{8}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
\end{itemize}
In general, the result gives the full spectrum of operator dimensions in the ${\rm DN}$ to $\lambda $ transition. In the bosonic theory we consider, the primary fields are vertex operators, which is exponential of the field $\exp( \nu \phi )$. Depending on the convention, the dimension of the vertex operator is a numerical constant times $\frac{\nu^2}{8\pi}$. So if $\nu$ linearly depend on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points we work out above. In a rational boson theory, the number of primary fields is finite. It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.

On the other hand, in our lattice boson model, $\theta$ parameterizes the bond interaction between the boundary sites of the chains. Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means the $\Sigma$ matrix is closer to the original, thus a smaller perturbation and vise versa. Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) of the result.

>>>>

For the more interesting case where the boundary condition are of the same type, we have verified the quadratic angle dependence numerically for ${\rm DN} \rightarrow \lambda$ {\iffalse \color{red}the process in Eq.~\eqref{eq:DNDN}.\fi}. We can first understand the values of several special points on this curve. 
\begin{itemize}
\item $\theta = 0$: This is where the boundary condition does not change before and after the quench, so the Loschmidt echo stays at $1$ and hence the exponent is $0$.
\item $\theta = \frac{\pi}{2}$: This is the process ${\rm DN}\rightarrow {\rm  ND}$. The chain is still disconnected after the change of the boundary conditions. We can thus view the problem as changing the boundary conditions for two independent changes in Fig.~\ref{fig:echo}, one from D to N and the other from N to D. The Loschmidt echo can then be viewed as the product of the boundary two point correlation functions of the associated bcc operators $\phi_{\rm DN}$ and $\phi_{\rm ND}$, whose dimension is $\Delta = \frac{1}{16}$. From this we can get the exponent to be $\frac{1}{2}$,
\begin{equation}
\begin{aligned}
  \quad \mathcal{L}(\tau) &\sim |\langle \phi_{{\rm D N}}(0) \phi_{{\rm ND}}(\tau)   \rangle |^2 
|\langle \phi_{{\rm ND}}(0)  \phi_{{\rm DN}}(\tau)   \rangle| ^2\\
& \sim \frac{1}{|\tau|^{8\Delta}} = \frac{1}{|\tau|^{\frac{1}{2}}},
\end{aligned}
\end{equation}
which agrees with our results. 
\item $\theta = \frac{\pi}{4}$: This is the process ${\rm DN}\rightarrow {\rm P}$. The exponent $\frac{3}{8}$ agrees with the Ref.~\onlinecite{kennes_universal_2014,stephan_logarithmic_2013}, where the difference with the exponent $\frac{1}{4}$ of ${\rm DD} \rightarrow {\rm P}$ is interpreted as twice the dimension of bcc operator dimension ($\frac{1}{16}$) that transforms D to N.
\end{itemize}
In general, the result gives the full spectrum of operator dimensions in the ${\rm DN}$ to $\lambda $ transition. In the bosonic theory we consider, the primary fields are vertex operators, which is exponential of the field $\exp( \nu \phi )$. Depending on the convention, the dimension of the vertex operator is a numerical constant times $\frac{\nu^2}{8\pi}$. So if $\nu$ linearly depend on $\theta$ (or $x$), then we will end up with a quadratic relation whose expression can already be fixed by the three special points we work out above. In a rational boson theory, the number of primary fields is finite. It requires further exploration to identify these bcc operators with the existing primary fields and their physical significance.

On the other hand, in our lattice boson model, $\theta$ parameterizes the bond interaction between the boundary sites of the chains. Consequently it characterizes the strength of the local perturbation to the Hamiltonian: smaller $\theta$ means the $\Sigma$ matrix is closer to the original, thus a smaller perturbation and vise versa. Therefore, we expect that a larger perturbation will result in a faster decay of the Loschmidt echo, which is reflected by the monotonically increasing decay exponent (the absolute value of the exponent) in the figures.
